---
title: "Lab 00 - Hello IDS!"
author: "Harris Lovatt"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Donnie Darko", "DanTDM", 
           "Walter White", "Fleabag"),
  github_username = c("mcgregors-garden", "Ass_Film", "Dr_Tryaurus", 
                      "Meth_Maker", "ILOVEPRIEST"), 
  colour = c("powderblue", "violetred4", "turquoise2", 
             "steelblue4", "pink3"),
  hobby = c("Hopping", "being depressed", "mining", 
            "drug dealing", "sex"),
  favourite_number = c(2, 5, 4, 7, 9)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Each members favourite number and username

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite Number",
          title = "Favourite Number of each Username")
```

Adds labels to the graph

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A table would probably be the best way to show this information
